Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber}}

### 2018-03-16 Paper.tex

Let $G_T$ be the multiplicative abelian group underlying $F_{q^{12}}$. It is known that a non-degenerate bilinear map $e : G_1\times G_2 \to G_T$ exists.
This bilinear map is a type three pairing. Let $P_T = e(P_1, P_2)$, $a$ be a set of $k$ points in $G_1$, and $b$ be a set of $k$ points that are in $G_2$. It follows from the definition of a pairing that the following are equivalent
\begin{eqnarray} \label{eq:pairing-check}
\log_{P_1}(a_1)\times\log_{P_2}(b_1)+\cdots+\log_{P_1}(a_{k})\times\log_{P_2}(b_{k})&\equiv& 1\mod q\\
\prod_{i=0}^{k}e\left(a_i, b_i\right) &=& P_T
\end{eqnarray}
Thus the pairing check provides a method to verify \ref{eq:pairing-check}.

A 32 byte number $\mathbf{x}\in\mathbf{P}_{256}$ might and might not represent an element of $F_{\mathrm{p}}$.
\begin{equation}
\delta_{\mathrm{p}}(\mathbf x)\equiv\begin{cases}
\mathbf x&\text{if}\ \mathbf x<p\\
\varnothing&\text{otherwise}
\end{cases}
\end{equation}

A 64 byte data $\mathbf x\in\mathbf B_{512}$ might and might not represent an element of $G_1$.
\begin{eqnarray}
\delta_1(\mathbf x)&\equiv&\begin{cases}
g_1&\text{if}\ g_1\in G_1\\
\varnothing&\text{otherwise}
\end{cases}\\
g_1&\equiv&\begin{cases}
(x,y)&\text{if}\ x\neq\varnothing\wedge y\neq\varnothing\\
\varnothing&\text{otherwise}
\end{cases}\\
x&\equiv&\delta_{\mathrm{p}}(\mathbf x[0..31])\\
y&\equiv&\delta_{\mathrm{p}}(\mathbf x[32..63])
\end{eqnarray}

A 128 byte data $\mathbf x\in\mathbf B_{1024}$ might and might not represent an element of $G_2$.
\begin{eqnarray}
\delta_2(\mathbf x)&\equiv&\begin{cases}
g_2&\text{if}\ g_2\in G_2\\
\varnothing&\text{otherwise}
\end{cases}\\
g_2&\equiv&\begin{cases}
((x_0i+y_0),(x_1i+y_1))&\text{if}\ x_0\neq\varnothing\wedge y_0\neq\varnothing\wedge x_1\neq\varnothing\wedge y_1\neq\varnothing\\
\varnothing&\text{otherwise}
\end{cases}\\
x_0&\equiv&\delta_{\mathrm{p}}(\mathbf x[0..31])\\
y_0&\equiv&\delta_{\mathrm{p}}(\mathbf x[32..63])\\
x_1&\equiv&\delta_{\mathrm{p}}(\mathbf x[64..95])\\
y_1&\equiv&\delta_{\mathrm{p}}(\mathbf x[96..127])
\end{eqnarray}

We define $\Xi_{\mathtt{SNARKV}}$ as a precompiled contract which checks if \ref{eq:pairing-check} holds, for intended use in zkSNARK verification.

\begin{eqnarray}
\Xi_{\mathtt{SNARKV}}&\equiv&\Xi_{\mathtt{PRE}}\quad\text{except:}\\
\qquad\Xi_{\mathtt{SNARKV}}(\boldsymbol\sigma,g,I)&=&\left(\varnothing,0,A^0,()\right)\quad\text{if}\ F\\
F&\equiv&(|I_{\mathbf{d}}|\bmod 192\neq 0\vee(\exists j.\ a_{\mathrm{j}}=\varnothing\vee b_{\mathrm{j}}=\varnothing))\\
k &=& \dfrac{|I_{\mathbf{d}}|}{192} \\
g_{\mathrm{r}}&=& 60000k + 40000 \\
\mathbf o[0..31]&\equiv&\begin{cases}
0x0000000000000000000000000000000000000000000000000000000000000001&\text{if}\ v\wedge\neg F\\
0x0000000000000000000000000000000000000000000000000000000000000000&\text{if}\ \neg v\wedge\neg F
\end{cases}\\
v&\equiv&(\log_{P_1}(a_1)\times\log_{P_2}(b_1)+\cdots+\log_{P_1}(a_{\mathrm{k}})\times\log_{P_2}(b_{\mathrm{k}})\equiv 1\mod q)\\
a_1&\equiv&\delta_1(I_{\mathbf d}[0..63])\\
b_1&\equiv&\delta_2(I_{\mathbf d}[64..191])\\\nonumber
\vdots\\
a_{\mathrm{k}}&\equiv&\delta_1(I_{\mathbf d}[(|I_{\mathbf d}|-192)..(|I_{\mathbf d}|-129)])\\
b_{\mathrm{k}}&\equiv&\delta_2(I_{\mathbf d}[(|I_{\mathbf d}|-128)..(|I_{\mathbf d}|-1)])
\end{eqnarray}

@@

\linkdest{invalidsig}We declare that a signature is invalid unless all the following conditions are true:
\begin{align}
0 < \linkdest{r}{r} &< \mathtt{\tiny secp256k1n} \\
0 < \linkdest{s}{s} &< \mathtt{\tiny secp256k1n} \div 2 + 1 \\
\hyperlink{v}{v} &\in \{27,28,\mathtt{\tiny chain\_{\mathrm{id}}} \times 2 + 35, \mathtt{\tiny chain\_{\mathrm{id}}} \times 2 + 36\}
\end{align}
where:
\begin{align}
\mathtt{\tiny secp256k1n} &= 115792089237316195423570985008687907852837564279074904382605163141518161494337
%\mathtt{\tiny secp256k1p} &= 2^{256} - 2^{32} - 977\\
\end{align}

@@

\hypertarget{h_of_T}{}The message hash, $h(T)$, to be signed is the Keccak hash of the transaction. Two different flavors of signing schemes are available. One operates without the latter three signature components, formally described as $T_{\mathrm{r}}$, $T_{\mathrm{s}}$ and $T_{\mathrm{w}}$. The other operates on nine elements:
\begin{eqnarray}
L_{S}(T) & \equiv & \begin{cases}
(T_{\mathrm{n}}, T_{\mathrm{p}}, T_{\mathrm{g}}, T_{\mathrm{t}}, T_{\mathrm{v}}, \mathbf{p}) & \text{if} \; v \in \{27, 28\} \\
(T_{\mathrm{n}}, T_{\mathrm{p}}, T_{\mathrm{g}}, T_{\mathrm{t}}, T_{\mathrm{v}}, \mathbf{p}, \mathtt{\tiny chain\_{\mathrm{id}}}, (), ()) & \text{otherwise} \\
\end{cases} \\
\nonumber \text{where} \\
\nonumber \mathbf{p} & \equiv & \begin{cases}
T_{\mathbf{i}} & \text{if}\ T_{\mathrm{t}} = 0 \\
T_{\mathbf{d}} & \text{otherwise}
\end{cases} \\
h(T) & \equiv & \mathtt{\small KEC}( L_{S}(T) )
\end{eqnarray}

>>>>

A 32 byte number $\mathbf{x}\in\mathbf{P}_{256}$ might and might not represent an element of $F_{\mathrm{p}}$.
\begin{equation}
\delta_{\mathrm{p}}(\mathbf{x})\equiv\begin{cases}
\mathbf{x}&\text{if}\ \mathbf{x}<p\\
\varnothing&\text{otherwise}
\end{cases}
\end{equation}

A 64 byte data $\mathbf{x}\in\mathbf{B}_{512}$ might and might not represent an element of $G_1$.
\begin{eqnarray}
\delta_1(\mathbf{x})&\equiv&\begin{cases}
g_1&\text{if}\ g_1\in G_1\\
\varnothing&\text{otherwise}
\end{cases}\\
g_1&\equiv&\begin{cases}
(x,y)&\text{if}\ x\neq\varnothing\wedge y\neq\varnothing\\
\varnothing&\text{otherwise}
\end{cases}\\
x&\equiv&\delta_{\mathrm{p}}(\mathbf{x}[0..31])\\
y&\equiv&\delta_{\mathrm{p}}(\mathbf{x}[32..63])
\end{eqnarray}

A 128 byte data $\mathbf{x}\in\mathbf{B}_{1024}$ might and might not represent an element of $G_2$.
\begin{eqnarray}
\delta_2(\mathbf{x})&\equiv&\begin{cases}
g_2&\text{if}\ g_2\in G_2\\
\varnothing&\text{otherwise}
\end{cases}\\
g_2&\equiv&\begin{cases}
((x_0i+y_0),(x_1i+y_1))&\text{if}\ x_0\neq\varnothing\wedge y_0\neq\varnothing\wedge x_1\neq\varnothing\wedge y_1\neq\varnothing\\
\varnothing&\text{otherwise}
\end{cases}\\
x_0&\equiv&\delta_{\mathrm{p}}(\mathbf{x}[0..31])\\
y_0&\equiv&\delta_{\mathrm{p}}(\mathbf{x}[32..63])\\
x_1&\equiv&\delta_{\mathrm{p}}(\mathbf{x}[64..95])\\
y_1&\equiv&\delta_{\mathrm{p}}(\mathbf{x}[96..127])
\end{eqnarray}

We define $\Xi_{\mathtt{SNARKV}}$ as a precompiled contract for zkSNARK verification.
\begin{eqnarray}
\Xi_{\mathtt{SNARKV}}&\equiv&\Xi_{\mathtt{PRE}}\quad\text{except:}\\
\qquad\Xi_{\mathtt{SNARKV}}(\boldsymbol\sigma,g,I)&=&\left(\varnothing,0,A^0,()\right)\quad\text{if}\ F\\
F&\equiv&(|I_{\mathbf{d}}|\bmod 192\neq 0\vee(\exists j.\ a_{\mathrm{j}}=\varnothing\vee b_{\mathrm{j}}=\varnothing))\\
k &=& \dfrac{|I_{\mathbf{d}}|}{192} \\
g_{\mathrm{r}}&=& 60000k + 40000 \\
\mathbf{o}[0..31]&\equiv&\begin{cases}
0x0000000000000000000000000000000000000000000000000000000000000001&\text{if}\ v\wedge\neg F\\
0x0000000000000000000000000000000000000000000000000000000000000000&\text{if}\ \neg v\wedge\neg F
\end{cases}\\
v&\equiv&(\log_{P_1}(a_1)\times\log_{P_2}(b_1)+\cdots+\log_{P_1}(a_{\mathrm{k}})\times\log_{P_2}(b_{\mathrm{k}})\equiv 1\mod q)\\
a_1&\equiv&\delta_1(I_{\mathbf{d}}[0..63])\\
b_1&\equiv&\delta_2(I_{\mathbf{d}}[64..191])\\\nonumber
\vdots\\
a_{\mathrm{k}}&\equiv&\delta_1(I_{\mathbf{d}}[(|I_{\mathbf{d}}|-192)..(|I_{\mathbf{d}}|-129)])\\
b_{\mathrm{k}}&\equiv&\delta_2(I_{\mathbf{d}}[(|I_{\mathbf{d}}|-128)..(|I_{\mathbf{d}}|-1)])
\end{eqnarray}

@@

\linkdest{invalidsig}We declare that a signature is invalid unless all the following conditions are true:
\begin{align}
0 < \linkdest{r}{r} &< \mathtt{\tiny secp256k1n} \\
0 < \linkdest{s}{s} &< \mathtt{\tiny secp256k1n} \div 2 + 1 \\
\hyperlink{v}{v} &\in \{27,28,\mathtt{\tiny chain\_id} \times 2 + 35, \mathtt{\tiny chain\_id} \times 2 + 36\}
\end{align}
where:
\begin{align}
\mathtt{\tiny secp256k1n} &= 115792089237316195423570985008687907852837564279074904382605163141518161494337
%\mathtt{\tiny secp256k1p} &= 2^{256} - 2^{32} - 977\\
\end{align}

@@

\hypertarget{h_of_T}{}The message hash, $h(T)$, to be signed is the Keccak hash of the transaction. Two different flavors of signing schemes are available. One operates without the latter three signature components, formally described as $T_{\mathrm{r}}$, $T_{\mathrm{s}}$ and $T_{\mathrm{w}}$. The other operates on nine elements:
\begin{eqnarray}
L_{S}(T) & \equiv & \begin{cases}
(T_{\mathrm{n}}, T_{\mathrm{p}}, T_{\mathrm{g}}, T_{\mathrm{t}}, T_{\mathrm{v}}, \mathbf{p}) & \text{if} \; v \in \{27, 28\} \\
(T_{\mathrm{n}}, T_{\mathrm{p}}, T_{\mathrm{g}}, T_{\mathrm{t}}, T_{\mathrm{v}}, \mathbf{p}, \mathtt{\tiny chain\_id}, (), ()) & \text{otherwise} \\
\end{cases} \\
\nonumber \text{where} \\
\nonumber \mathbf{p} & \equiv & \begin{cases}
T_{\mathbf{i}} & \text{if}\ T_{\mathrm{t}} = 0 \\
T_{\mathbf{d}} & \text{otherwise}
\end{cases} \\
h(T) & \equiv & \mathtt{\small KEC}( L_{S}(T) )
\end{eqnarray}
